No-click browsing of large hierarchical data

### 2020-05-27 paper/HCC2020-short/paper.tex
IEEE Copyright notice追加

\author{\IEEEauthorblockN{Toshiyuki Masui}
  \IEEEauthorblockA{
    \textit{Keio University} \\
    \textit{Faculty of Environment and Information Studies}\\
    5322 Endo, Fujisawa, Kanagawa 252-0882 Japan \\
    masui@pitecan.com
  }
}

@@

@@

Finding a data from a huge hierarchical database takes time
because users should traverse the tree using a mouse or a keyboard,
and click a ``select'' button to check the content.
If the data was not appropriate,
they should go to the next entry and perform the selection task again.

@@

\begin{enumerate}
\item A portion of hierarchical data is shown to the user as a list.

@@

We show how Gear works, using a hierarchical data structure of
a shops list in a shopping mall shown in Figure \ref{fig1} as example data.
A rectangles with a thick border represent shop categories, and
other rectangles represent individual shops.

@@

To prove that Gear is useful for selecting an entry from a
large hierarchical database,
we have developed the ``\tsf{\SC}'' service\footnote{
  \tsf{https://serencast.com/}
}, where users can enjoy movies, musics, and other web services
on the browser with the Gear interface without clicking an entry.
{\SC} is implemented in JavaScript and runs on modern web browsers.
%
{\SC} uses the ``\tsf{\SB}'' wiki service\footnote{
  \tsf{https://Scrapbox.io/}
} for listing the contents of the hierarchical database.
{\SB} is an interactive wiki
system where users can share and edit texts on the web browser,
just like the Google Docs system.

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=65mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
  \caption{Watching ``Breakfast at Tiffany's''.}
  \label{tiffany}
\end{figure}

@@

In one page, we can specify a hierarchical structure by using indentations.
Figure \ref{musiclist} shows a portion of a list of music CDs and
titles by ``Weather Report'' and ``Wes Montgomery'' are shown\footnote{
  Weather Report is the name of a famous Jazz group, and Wes Montgomery is a famous Jazz guitarist.
}.
For example, 
``Black Market'' is the first title in the album ``8:30'' of ``Weather Report'', and
``Scarlet Woman'' follows ``Black Market''.
``Wes Montgomery'' is listed in the same layer as ``Weather Report'', and
the album ``Tequilla'' is listed one level below the level of the name of the artist.
%
The title of {\SB} page shown in Figure \ref{musiclist} is ``Music'', and 
we can collect Movie page, Music page, and other pages by
listing them in another page (``Top'' page) shown in Figure \ref{top}.

\begin{figure}[H]
 \begin{minipage}{0.45\hsize}
  \centerline{\includegraphics[width=30mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
  \caption{Music list.}
  \label{musiclist}
 \end{minipage}
 \begin{minipage}{0.45\hsize}
  \centerline{\includegraphics[width=22mm,bb=0 0 262 515]{figures/5a644f357ba6a6b81b011e200019d736.png}}
  \caption{Top page.}
  \label{top}
 \end{minipage}
\end{figure}

Many {\SB} pages (Music, Movies, etc.) are listed in the Top page, and
the pages are treated as children pages of the Top page.
By constructing data hierarchically like this,
We can build a very large hierarchical database for watching movies, videos, news, etc.
A hierarchical database with
As many as 100,000 pages can be easily constructed on {\SB}, and
we can select one of the entries only by using {\up} and {\down} keys,
with the Gear technique described in section \ref{navigation}.

\comment{
\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackmarket.png}}
\caption{Playing a music.}
\label{blackmarket}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackjack.png}}
\caption{Reading a comic book.}
\label{blackjack}
\end{figure}
}

Since anybody can edit {\SB} pages and construct the hierarchical data,
people can enjoy creating their own database by editing their {\SB} pages.
When someone wants to advertise their works,
he can create his {\SB} pages
and give them to other people so that they can watch the pages.
People can freely include other people's {\SB} pages in their own list
and enjoy all the contents just by using Gear.

@@

The simplest input device for Gear may be keyboards and push buttons.
Gear works pretty comfortably with arrow keys on a PC.
Various HID devices\footnote{
  \tsf{https://en.wikipedia.org/wiki/Human\_interface\_device}
} are available on the market, and
all such devices can be used as an input device for Gear.

@@

We have also tried to use a paddle-like device for generating {\up} and {\down}.
Users can push the puddle to the right to generate {\up} and
left to generate {\down}.
Pressure sensors are installed on the puddle, and
many {\up}'s are generated when the user pushes the puddle strongly.

\begin{figure}[H]
  \centerline{\includegraphics[width=38mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
  \caption{Paddle device for Gear.}
  \label{paddle}
\end{figure}

@@

Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
For example, ``jog dials'' have been widely used for controlling VCRs, and we tried the device for Gear.

\begin{figure}[H]
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=38mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
    \caption{Using a jog dial.}
    \label{jog}
  \end{minipage}
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=38mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
    \caption{A disk-based device for Gear.}
    \label{disk}
  \end{minipage}
\end{figure}

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=38mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
  \caption{Using a roller.}
  \label{roller}
\end{figure}

@@

To compare the speed of Gear with conventional navigation method,
we created two applications for checking how fast a user can select an entry
from a large hierarchical database.
%
Both applications behaves the same way:
a user can set the date to a specific time to see a photo in a 15-minute monorail trip.
%
Using the first one (App1), a user can set the time using Gear (Figure \ref{monorailgear})
with up/down arrow keys for {\up} and {\down}.

@@

\begin{figure}[H]
\centerline{
  \includegraphics[width=39mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
  \includegraphics[width=39mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
}
\caption{Average search time of App1 and App2.}
\label{monorailtime}
\end{figure}

@@

It seems to be a good idea to use Gear on more conventional visualization techniques like
TreeView\footnote{
  \textsf{http://en.wikipedia.org/wiki/Tree\_view}
}, by replacing 4-way navigation with Gear.

\comment{
  \begin{figure}[H]
    \centerline{
      \includegraphics[width=38mm,bb=0 0 188 188]{figures/treeview.png}
    }
    \caption{A TreeView example.}
    \label{treeview}
  \end{figure}
}

% LensBar\cite{Masui:1998:LVB:647341.721215}
% is also a ZUI system for handling large hierarchical data,
% but the same data structure used in LensBar can be used for Gear.
% Users can use a pointing devices when it is appropriate,
% and use two keys or a disk device when pointing devices is not available.

\comment{
\subsection{Timing control}

The biggest disadvantage of Gear is that
the behavior of Gear depends on the speed of the user's operations.
In Figure \ref{fig4},
if a user wanted to select \tsf{Clothing} but couldn't issue {\down}
quickly enough, he will see Figure \ref{fig5} instead of Figure \ref{fig7}.
This is a tradeoff between usability and simplicity, and
the best parameter should be set based on the user and the Gear device.

\subsection{Is the Gear interface new?}

Since the idea of Gear interface is so simple,
we have been wondering if the same idea existed in the past.
%
We could not find a research paper on 
navigation techniques based on two keys.
Many key-based navigation techniques are found on patent database,
but we could not find a navigation method based on two keys.
We are almost sure that The Gear interface had never been popular before.
}

@@

One of the authors have been using Gear in his living room for several years
with a small personal computer connected to a 60-inch TV monitor.
The database is managed on {\SB}, and
a mouse wheel of a wireless Bluetooth mouse is used for Gear interface.
With Gear, the user can enjoy all available contents on the web with the mouse wheel
without selecting the source of the movies, animes, and musics from Amazon, Netflix, etc.

@@

\comment{
Large dictionary database can also be treated as a large
hierarchical data, since the name of the entry can be treated hierarchically:
e.g. an entry for ``\tsf{dictionary}'' can be stored under ``\tsf{d}'', ``\tsf{d/i}'', and so on.

No formal evaluation have been done yet, but Gear has been used in the author's
living room for six months, and the author's family members are using it
everyday for watching anime films and listening to music.
Besides PowerMate, a wireless mouse is also used,
since we can carry it anywhere and select
a film or a music just by rotating the mouse wheel.
}

We demonstrated Gear at an exhibition
% held in November 2013,
and asked more than 100 people to try it
(Figure \ref{exhibition}).
%
Since the only thing a user can do with Gear was to rotate a wheel,
users seemed to be able to understand the behavior of Gear with trials and errors.
% 
% a user can use the device and see what happens without thinking about
% other interactions.
% 
Using only one rotating device for data navigation is a new experience for
all the visitors, but the hard restriction of the device seemed to have worked in this case.

\begin{figure}[H]
\centerline{\includegraphics[width=84mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right using a wheel device at an exhibition.}
\label{exhibition}
\end{figure}

@@

We have developed a new simple interaction method ``Gear'' for exploring
large hierarchical data structure.
A Gear user can easily find an entry in a huge hierarchical database
only by using a rotating input device which can be installed at
wide range of locations where conventional keyboards and switches do not fit.
We are hoping to install various implementations of Gear and try them at
various places like kitchens, restrooms, etc.

>>>>

\author{\IEEEauthorblockN{Toshiyuki Masui}
  \IEEEauthorblockA{
    % \textit{Faculty of Environment and Information Studies}\\
    \textit{Keio University} \\
    % Fujisawa, Japan \\
    5322 Endo, Fujisawa, Kanagawa 252-0882, Japan \\
    masui@pitecan.com
  }
}

\IEEEoverridecommandlockouts
\IEEEpubid{\makebox[\columnwidth]{978-1-7281-6901-9/20/\$31.00~\copyright2020 IEEE\hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

@@

\IEEEpubidadjcol

@@

Finding data from a huge hierarchical database takes time
because users should traverse the tree using a mouse or a keyboard,
and click a ``select'' button to check the content.
If the data was not appropriate,
they should go to the next entry and perform the selection task again.

@@

\begin{enumerate}
\item A portion of hierarchical data is shown to the user.

@@

We show how Gear works, using a hierarchical data structure of
a shop list in a shopping mall shown in Figure \ref{fig1} as example data.
A rectangles with a thick border represents a shop category, and
other rectangles represent individual shops.

@@

To prove that Gear is useful for selecting an entry from a
large hierarchical database,
we developed the ``\tsf{\SC}'' service\footnote{
  \tsf{https://Serencast.com/}
}, where users can enjoy movies, musics, and other web services
on the browser with the Gear interface without clicking an entry.
{\SC} is implemented in JavaScript and runs on modern web browsers.
%
{\SC} uses the ``\tsf{\SB}'' wiki service\footnote{
  \tsf{https://Scrapbox.io/}
} for listing the contents of the hierarchical database.
{\SB} is an interactive wiki
system where users can share and edit texts on the web browser,
just like the Google Docs system.

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=65mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
  \caption{Watching ``Breakfast at Tiffany's'' on Serencast.}
  \label{tiffany}
\end{figure}

@@

Since anybody can edit {\SB} pages and construct the hierarchical data,
people can enjoy creating their own database by editing their {\SB} pages.
When someone wants to advertise their works,
he can create his {\SB} pages
and give them to other people so that they can watch the pages.

@@

The simplest input device for Gear may be keyboards and push buttons.
Gear works pretty comfortably with arrow keys on a PC.
Various HID devices\footnote{
  \tsf{https://en.wikipedia.org/wiki/Human\_interface\_device}
} are available on the market, and
all such devices can be used as input devices for Gear.

@@

We have also tried to use a paddle-like device for generating {\up} and {\down} (Figure \ref{paddle}).
Users can push the puddle to the right to generate {\up} and
left to generate {\down}.
Pressure sensors are installed on the puddle, and
many {\up}'s are generated when the user pushes the puddle strongly.

\begin{figure}[H]
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=38mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
    \caption{Paddle device for Gear.}
    \label{paddle}
  \end{minipage}
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=38mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
    \caption{Using a jog dial.}
    \label{jog}
  \end{minipage}
\end{figure}

@@

Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
For example, ``jog dials'' have been widely used for controlling VCRs,
and we tried the device for Gear (Figure \ref{jog}).

\begin{figure}[H]
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=38mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
    \caption{A disk-based device for Gear.}
    \label{disk}
  \end{minipage}
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=38mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
    \caption{Using a roller.}
    \label{roller}
  \end{minipage}
\end{figure}

@@

@@

To compare the speed of Gear with conventional navigation method,
we created two applications for checking how fast a user can select an entry
from a large hierarchical database.
%
Both applications behaves the same way:
a user can set the date to a specific time to see a photo in a 15-minute monorail trip.
%
Using the first one (App1), a user can set the time using Gear
with up/down arrow keys for {\up} and {\down} (Figure \ref{monorailgear}).

@@

\begin{figure}[H]
\centerline{
  \includegraphics[width=43mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
  \includegraphics[width=43mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
}
\caption{Average search time of App1 and App2.}
\label{monorailtime}
\end{figure}

@@

It seems to be a good idea to use Gear on more conventional visualization techniques like
TreeView\footnote{
  \textsf{http://en.wikipedia.org/wiki/Tree\_view}
}, where 4 keys are used for navigation.
%
We can also use Gear on a 1D zooming system like
LensBar\cite{Masui:1998:LVB:647341.721215},
where pointing devices are mainly used for navigation.

% is also a ZUI system for handling large hierarchical data,
% but the same data structure used in LensBar can be used for Gear.
% Users can use a pointing devices when it is appropriate,
% and use two keys or a disk device when pointing devices is not available.

@@

The author have been using Gear in his living room for several years
with a small personal computer connected to a 60-inch TV monitor.
The database is managed on {\SB}, and
a mouse wheel of a wireless Bluetooth mouse is used for Gear interface.
With Gear, the user can enjoy all available contents on the web with the mouse wheel
without selecting the source of the movies, animes, and musics from Amazon, Netflix, etc.

@@

We demonstrated Gear at an exhibition
and asked more than 100 people to try it
(Figure \ref{exhibition}).
%
Since the only thing a user can do with Gear was to rotate a wheel,
users seemed to be able to understand the behavior of Gear with trials and errors.
% 
% a user can use the device and see what happens without thinking about
% other interactions.
% 
Using only one rotating device for data navigation is a new experience for
all the visitors, but the hard restriction of the device seemed to have worked in this case.

\begin{figure}[H]
\centerline{\includegraphics[width=50mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{People at the right using a wheel device at an exhibition.}
\label{exhibition}
\end{figure}

@@

We have developed a new simple interaction method ``Gear'' for exploring
a large hierarchical data structure.
A Gear user can easily find an entry in a huge hierarchical database
only by using two keys or a rotating device that can be installed at
wide range of locations where conventional keyboards and switches do not fit.
We are hoping to install various implementations of Gear and try them at
various places like kitchens, restrooms, etc.
